A general and efficient representation of Ancestral Recombination Graphs

### 2022-08-02 paper.tex
ASG redraft

% JK: This paragraph is weak, and needs some work. Basically want to
% illustrate the mathematical literature which views ancestral
% graphs very much as *processes*.
However, in parallel with this tendancy to decouple the term
Ancestral Recombination graph from its original defining stochastic process,
an extensive mathematical literature has developed in
studying other related stochastic processes encoded via a graph.
In particular, the Ancestral Selection Graph
(ASG)~\citep{krone1997ancestral,neuhauser1997genealogy}
uses a similar approach to model an ensemble of correlated
potential ancestral trees and has been of considerable
and ongoing theoretical interest~\citep[e.g.][]{
neuhauser1999ancestral,
donnelly1999genealogical,
fearnhead2001perfect,
fearnhead2003ancestral,
etheridge2009coalescent,
gonzalezcasanova2018duality,
koskela2019robust}.
A vital distinction between the ARG (process) and ASG, however,
is that there is a hard distinction between the stochastic process
(the graph) and an observable realisation (a single tree) in the ASG
because the it encodes \emph{potential} ancestral trees.
Similarly, the Ancestral Gene Transfer Graph
models horizontal gene transfer~\citep{baumdicker2014infinitely}
by [FINISH ME. Also, any other ASG-like \emph{processes} to mention?].

>>>>

% JK: This paragraph is weak, and needs some work. Basically want to
% illustrate the mathematical literature which views ancestral
% graphs very much as *processes*.
% Jere: ASG section redrafted, gene transfer left as TODO (because I
% know essentially nothing about it).
In parallel with this tendancy to decouple the term
Ancestral Recombination Graph from its original defining stochastic process,
an extensive mathematical literature has developed in
studying other related stochastic processes encoded via a graph.
In particular, the Ancestral Selection Graph
(ASG)~\citep{krone1997ancestral,neuhauser1997genealogy}
uses a similar approach to model natural selection.
Unlike the ARG process, the ASG imposes a hard distinction between the stochastic process,
which constructs a random ARG-like graph, and an observable realisation,
which is a single tree sampled from the graph in a non-uniform way to encode desired
patterns of natural selection. 
Constructions of ASG-like stochastic processes encoding various
forms of selection, often in parallel with recombination or other genetic forces,
are an area of considerable and ongoing theoretical interest~\citep[e.g.][]{
neuhauser1999ancestral,
donnelly1999genealogical,
fearnhead2001perfect,
fearnhead2003ancestral,
etheridge2009coalescent,
gonzalezcasanova2018duality,
koskela2019robust}.
Similarly, the Ancestral Gene Transfer Graph
models horizontal gene transfer~\citep{baumdicker2014infinitely}
by [FINISH ME.
